\begin{thebibliography}{10}

\bibitem{MOA}
Albert Bifet, Geoff Holmes, Richard Kirkby, and Bernhard Pfahringer.
\newblock Moa massive online analysis, 2010.
\newblock \url{http://mloss.org/software/view/258/}.

\bibitem{WEKA}
Mark Hall, Eibe Frank, Geoffrey Holmes, Bernhard Pfahringer, Reutemann Peter,
  and Ian~H. Witten.
\newblock The weka data mining software: An update.
\newblock {\em SIGKDD Explorations}, 11(1), 2009.

\bibitem{Thesis}
Jesse Read.
\newblock {\em Scalable Multi-label Classification}.
\newblock PhD thesis, University of Waikato, 2010.

\bibitem{MEDS2}
Jesse Read, Albert Bifet, Bernhard Pfahringer, and Geoffrey Holmes.
\newblock Scalable and efficient multi-label classification for evolving data
  streams.
\newblock {\em Machine Learning}, 2012.
\newblock Accepted for publication.

\bibitem{EPS}
Jesse Read, Bernhard Pfahringer, and Geoff Holmes.
\newblock Multi-label classification using ensembles of pruned sets.
\newblock In {\em ICDM'08: Eighth IEEE International Conference on Data
  Mining}, pages 995--1000. IEEE, 2008.

\bibitem{ECC2}
Jesse Read, Bernhard Pfahringer, Geoffrey Holmes, and Eibe Frank.
\newblock Classifier chains for multi-label classification.
\newblock {\em Machine Learning}, 85(3):333--359, 2011.

\bibitem{MMD}
G.~Tsoumakas, I.~Katakis, and I.~Vlahavas.
\newblock Mining multi-label data.
\newblock In O.~Maimon and L.~Rokach, editors, {\em Data Mining and Knowledge
  Discovery Handbook}. 2nd edition, Springer, 2010.

\bibitem{RAKEL}
Grigorios Tsoumakas and Ioannis~P. Vlahavas.
\newblock Random k-labelsets: An ensemble method for multilabel classification.
\newblock In {\em ECML '07: 18th European Conference on Machine Learning},
  pages 406--417. Springer, 2007.

\bibitem{UPM}
Julio~H. Zaragoza, Luis~Enrique Sucar, Eduardo~F. Morales, Concha Bielza, and
  Pedro Larra{\~n}aga.
\newblock Bayesian chain classifiers for multidimensional classification.
\newblock In {\em 24th International Conference on Artificial Intelligence
  (IJCAI '11)}, pages 2192--2197, 2011.

\bibitem{MT}
Bernard Zenko and Saso Dzeroski.
\newblock Learning classification rules for multiple target attributes.
\newblock In {\em PAKDD '08: Twelfth Pacific-Asia Conference on Knowledge
  Discovery and Data Mining}, pages 454--465, 2008.

\end{thebibliography}
